
%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%

\begin{thebibliography}{99}
\small

\bibitem{Abe} {\sc E. Abe},
   {\em Hopf algebras\/},
   Cambridge Univ.\ Press, London and New York (1977).

\bibitem{Schmudgen} {\sc A. Klimyk \&\ K. Schm\"udgen},
   {\em Quantum groups and their representations\/},
   Texts and Monographs in Physics, Springer-Verlag (1997).

\bibitem{Koelink:thesis} {\sc H.T. Koelink},
   {\em On quantum groups and $q$-special functions\/},
   Ph. D. thesis, Rijksuniv. Leiden (1991).

\bibitem{Koelink:QE2} {\sc H.T. Koelink},
   {\em The quantum group of plane motions and the Hahn-Exton $q$-Bessel function\/},
        Duke Math. Journal Vol. {\bf 76}, No. 2 (1994).

\bibitem{Koelink:Stokman} {\sc H.T. Koelink \&\ J.V. Stokman},
   {\em Fourier transforms on the quantum $SU(1,1)$ group\/},
    Institut de Math. de Jussieu, Unit\'e Mixte de Recherche 7586,
    Universit\'es Paris VI et Paris VII, {\sc cnrs},
    pr\'epublication 232 (1999).

\bibitem{KoelinkSwart:qBessel:zeros} {\sc H.T. Koelink \&\ R.F. Swtarttouw},
  {\em On the zeros of the Hahn-Exton $q$-Bessel function and associated $q$-Lommel
  polynomials\/}, J.\ Math.\ Anal.\ Appl.\ {\bf 186}, No. 3, 690-710 (1994).

\bibitem{Koornwinder} {\sc T.H. Koornwinder},
  {\em Special functions and $q$-commuting variables\/},
  Fields Institute communications, Vol.\ {\bf 14} (1997)

\bibitem{KoornwSwartt} {\sc T.H. Koornwinder \&\ R.F. Swarttouw},
  {\em On $q$-analogues of the Fourier and Hankel Transforms\/},
  Trans.\ Amer.\ Math.\ Soc.\ {\bf 333}, 445-461 (1992).

\bibitem{KV} {\sc J. Kustermans \&\ S. Vaes}
  {\em Locally compact quantum groups\/},
  preprint U.C. Cork \&\ K.U. Leuven (1999).

\bibitem{Jeroen:QE2:haar} {\sc J. Noels},
   {\em An algebraic framework for harmonic analysis
        on the quantum $E(2)$ group\/},
   Comm. in Algebra, 30(2), 693-743 (2002).

\bibitem{Swarttouw} {\sc R.F. Swarttouw},
  {\em The Hahn-Exton $q$-Bessel function\/},
  thesis, Technical University Delft (1992).

\bibitem{Fons:DPHA} {\sc A. Van Daele},
   {\em Dual pairs of Hopf $^*$-algebras\/},
   Bull.\ London Math.\ Soc.\ {\bf 25}, 209-230 (1993)
   \&\ Ext. version as lecture notes for a talk at
   univ. Orl\'eans, KU Leuven, Belgium (1991).

\bibitem{Fons:AFGD} {\sc A. Van Daele},
   {\em An algebraic framework for group duality\/},
   Adv.\ Math.\ {\bf 140} 323-366 (1998).

\bibitem{Fons:spectral_conditions} {\sc A. Van Daele},
   {\em The operator $a \tens b + b \tens a^{-1}$ when $ab=\lambda ba$\/},
   Preprint K.U. Leuven (1989).

\bibitem{FonsWor:QE2} {\sc A. Van Daele \&\ S.L. Woronowicz},
   {\em Duality for the Quantum $E(2)$ Group\/},
   Pacific Journal of Math.\ {\bf 173}, No.\ 2, 375-385 (1996).

\bibitem{Vainerman} {\sc L. Vainerman},
    {\em Gel'fand pair associated with the quantum group of motions
         of the plane and $q$-Bessel functions\/},
         Reports of Math.\ Phys.\ (1995).

\bibitem{VaksKor:QE2} {\sc L.L. Vaksman \& L.I.
         Korogodski\u{\i}},
         {\em An algebra of bounded functions on the quantum group of motions
              of the plane, and $q$-analogues of Bessel functions\/},
         Soviet Math. Dokl. {\bf 39}, 173-177 (1989).

\bibitem{wolfram} {\sc S. Wolfram},
  {\em Mathematica, a system for doing mathematics by computer\/},
  Addison-Wesley.

\bibitem{Wor:QE2} {\sc S.L. Woronowicz},
   {\em Quantum $E(2)$ group and its Pontryagin dual\/},
   Lett. in Math. Phys. {\bf 23}, 251-263 (1991)

\bibitem{Wor:Affiliated} {\sc S.L. Woronowicz},
   {\em  Unbounded elements affiliated with $C^*$algebras
         and non-compact quantum groups\/},
         Commun. Math. Phys. {\bf 136}, 399-432 (1991).

\end{thebibliography}

\end{document}

