
\begin{thebibliography}{99}
\bibitem{Abe}
   {\sc E. Abe},
   {\em Hopf algebras}\@.
   Cambridge Univ.\ Press, London and New York (1977).

\bibitem{Arens} {\sc R. Arens}
   {\em The adjoint of a bilinear operation\/},
   Proc.\ Amer.\ Math.\ Soc.\ {\bf 2}, 839-848 (1951).

\bibitem{Baaj:QE2} {\sc S. Baaj},
   {\em Repr\'esentation r\'eguli\`ere du groupe quantique $E_\mu(2)$ de Woronowicz}\@.
   Comptes Rendus Acad. Sci. Paris, S\'erie I {\bf 314}, 1021-1026 (1992).

\bibitem{BS}  {\sc S. Baaj \&\ G. Skandalis},
   {\em Unitaires multiplicatifs et dualit\'e pour les produits
        crois\'es de C$^*$-alg\`ebres}\@.
   Ann. scient. \'Ec. Norm. Sup., Serie 4, {\bf 26}, 425-488 (1993).

\bibitem{Bonsall_Duncan} {\sc F. F. Bonsall \&\ J. Duncan}
   {\em Complete Normed Algebras}\@.
   Ergebnisse de Mathematik und ihrer Grenzgebiete, Band 80, Springer-Verlag (1973).

\bibitem{civin_yood} {\sc P. Civin \&\ B. Yood},
   {\em The second conjugate space of a Banach algebra  as an algebra \/},
   Pac. J. Math. 11, 847-870 (1961).

\bibitem{FonsDra:QD} {\sc B. Drabant \&\ A. Van Daele},
   {\em Pairing and Quantum Double of Multiplier Hopf Algebras}\@.
   To appear in Algebras and Representation theory.

\bibitem{FonsDraZhang:actions}
   {\sc B. Drabant \&\ A. Van Daele \&\ Y. Zhang},
   {\em Actions of Multiplier Hopf Algebras}\@.
   Comm. in Algebra, {\bf 27}(9), 4117-4172 (1999).

\bibitem{EffrosRuan} {\sc E.G. Effros \&\ Z.-J. Ruan}
   {\em Discrete Quantum Groups I, the Haar measure}\@.
   Int. Journal of Math. 681-723 (1994).

\bibitem{Jarchow} {\sc H. Jarchow},
   {\em Locally Convex Spaces}\@.
   B.G. Teubner Stuttgart (1981).

\bibitem{Schmudgen} {\sc A. Klimyk \&\ K. Schm\"udgen},
   {\em Quantum groups and their representations}\@.
   Texts and Monographs in Physics, Springer-Verlag (1997).

\bibitem{Koelink:thesis} {\sc H.T. Koelink}
   {\em On quantum groups and $q$-special functions}\@.
   Ph. D. thesis, Rijksuniv. Leiden (1991).


\bibitem{Koelink:QE2} {\sc H.T. Koelink},
   {\em The quantum group of plane motions and the Hahn-Exton $q$-Bessel function\/},
        Duke Math. Journal Vol. {\bf 76}, No.\ 2 (1994).

\bibitem{Koelink:Stokman} {\sc H.T. Koelink \&\ J.V. Stokman},
   {\em Fourier transforms on the quantum $SU(1,1)$ group}\@.
    Institut de Math. de Jussieu, Unit\'e Mixte de Recherche 7586,
    Universit\'es Paris VI et Paris VII, {\sc cnrs},
    pr\'epublication 232 (1999).

\bibitem{KoelinkSwart:qBessel:zeros} {\sc H.T. Koelink \&\ R.F. Swarttouw},
   {\em On the zeros of the Hahn-Exton \mbox{$q$-Bessel}\ function and associated $q$-Lommel
   polynomials}\@. J.\ Math.\ Anal.\ Appl.\ {\bf 186}, No. 3, 690-710 (1994).

\bibitem{Koornwinder} {\sc Tom H. Koornwinder},
   {\em Special functions and $q$-commuting variables}\@.
   Fields Institute communications,  Amer. Math. Soc\@.  {\bf 14}, 131-166 (1997).

\bibitem{KoornwSwartt} {\sc T.H. Koornwinder \&\ R.F. Swarttouw},
   {\em On $q$-analogues of the Fourier and Hankel Transforms}\@.
   Trans.\ Amer.\ Math.\ Soc.\ {\bf 333}, 445-461 (1992).

\bibitem{Kothe} {\sc G. K\"othe}
   {\em Topological Vector Spaces, Vol. I \& II}
   Grundlehren der mathematischen Wissenschaften 237,
   Springer-Verlag, New York (1979).

\bibitem{Kust:Cstar} {\sc J. Kustermans \&\ A. Van Daele},
   {\em $C^*$-algebraic quantum groups arising from algebraic quantum groups}\@.
   Int. Journal of Math. Volume 8, {\bf 8}, 1067-1139 (1997).

\bibitem{Kust:thesis} {\sc J. Kustermans},
   {\em $C^*$-algebraic quantum groups arising from algebraic quantum groups}\@.
    Ph.\ D.\ thesis, K.U. Leuven (1996).

\bibitem{Kust:corep} {\sc J. Kustermans},
   {\em Examining the dual of an algebraic quantum group}\@.
   Preprint Odense Univ. \#funct-an/9704004 (1997).

\bibitem{KV} {\sc J. Kustermans \&\ S. Vaes}
   {\em Locally compact quantum groups}\@.
   To appear in: Annales Scient.\ de l'Ec. Norm. Sup. (1999).

\bibitem{KV:cr} {\sc J. Kustermans \&\ S. Vaes}
   {\em A simple definition for locally compact quantum groups}\@.
   C.R.\ Ac.\ Sc.\ Paris, Ser.\ I, {\bf 328}(10), 871-876 (1999).

\bibitem{KV:pnas} {\sc J. Kustermans \&\ S. Vaes}
   {\em The operator algebra approach to quantum groups}\@.
   Proc. Nat. Acad. Sci. U.S.A. (PNAS)
   Vol.\ {\bf 97}, No.\ 2, 547-552 (January 18, 2000).

\bibitem{Kust:universal} {\sc J. Kustermans \&\ A. Van Daele},
  {\em Universal $C^*$-algebraic quantum groups arising from algebraic quantum groups}\@.
   preprint Odense Univ. \#funct-an/9704006 (1997).

\bibitem{AnnFons} {\sc A. Maes \&\ A. Van Daele}
   {\em Notes on compact quantum groups}\@.
   Nieuw archief voor wiskunde, serie 4, deel {\bf 16}, No. 1-2, 73-112 (1998).

\bibitem{Majid} {\sc Shahn Majid}
   {\em Foundations of quantum group theory}\@.
   Cambrige university press (1995).

\bibitem{Montgomery} {\sc Susan Montgomery}
   {\em Hopf algebras and their actions on rings}\@.
   {\sc cbms}\ Regional Conf.\ Series in Math.\ {\bf 82}, AMS (1993).

\bibitem{Jeroen:QE2:Fourier} {\sc J. Noels},
   {\em Constructing Fourier transforms on the Quantum $E(2)$ group}\@.
   Preprint K.U. Leuven (2000)

\bibitem{Jeroen:QE2:haar} {\sc J. Noels},
   {\em An algebraic framework for harmonic analysis on the quantum $E(2)$ group}\@.
   Preprint K.U. Leuven (2000).

\bibitem{Schaefer} {\sc H.H. Schaefer},
   {\em Topological vector Spaces}\@.
   Macmillan Series in Advanced Mathematics and Theor.\ Phys.,
   New York (1966).

\bibitem{Swarttouw} {\sc R.F. Swarttouw},
  {\em The Hahn-Exton $q$-Bessel function}\@.
   Ph. D. thesis, Technical University Delft (1992).

\bibitem{Sweedler} {\sc M.E. Sweedler},
   {\em Hopf algebras}\@.
   Math.\ Lecture Notes Series, Benjamin, New York (1969).

\bibitem{Takesaki} {\sc M. Takesaki},
   {\em Theory of Operator Algebras I}\@.
   Springer-Verlag, New York (1979).

\bibitem{Treves} {\sc F. Treves},
   {\em Topological vector Spaces, Distributions and Kernels}\@.
   Academic Press, New York \&\ London (1967).

\bibitem{leonid:vainerman} {\sc L. Vainerman},
   {\em Gel'fand pair associated with the quantum group of motions of the plane and
        $q$-Bessel functions}\@. Reports of Math.\ Phys. (1995).

\bibitem{Fons:spectral_conditions} {\sc A. Van Daele},
   {\em The operator $a \tens b + b \tens a^{-1}$ when $ab=\lambda ba$}\@.
   Preprint K.U. Leuven (1989).

\bibitem{Fons:DPHA} {\sc A. Van Daele},
   {\em Dual pairs of Hopf $*$-algebras}\@.
   Bull.\ London Math.\ Soc.\ {\bf 25}, 209-230 (1993).

\bibitem{Fons:DQG} {\sc A. Van Daele},
   {\em Discrete Quantum Groups}\@.
   Journal of Algebra {\bf 180}, 431-444 (1996).

\bibitem{Fons:MHA} {\sc A. Van Daele},
   {\em Multiplier Hopf algebras}\@.
   Trans.\ Amer.\ Math.\ Soc.\ {\bf 342}, No.\ 2, 917-932, (1994).

\bibitem{Fons:AFGD} {\sc A. Van Daele},
   {\em An algebraic framework for group duality}\@.
   Adv.\ Math.\ {\bf 140} 323-366 (1998).

\bibitem{Fons:AFGD:proc} {\sc A. Van Daele},
   {\em Multiplier Hopf Algebras and Duality\/}
   Proceedings of the workshop on Quantum groups and quantum spaces
   (Warsaw, Nov.\ 1995).
   Banach Center Publ.\ {\bf 40}, 51-58,
   Inst.\ of Math., Polish Ac.\ of Sciences,
   Warszawa (1997).

\bibitem{Fons:pnas} {\sc A. Van Daele},
   {\em Quantum groups with invariant functionals}\@.
   Proc. Nat. Acad. Sci U.S.A. (PNAS) Vol.\ {\bf 97}, No.\ 2, 541-546 (January 18, 2000).

\bibitem{FonsZhang:DQG} {\sc A. Van Daele \&\ Y. Zhang},
   {\em Multiplier Hopf algebras of Discrete type}\@.
   Journal of algebra {\bf 214}, 400-417 (1999).

\bibitem{FonsZhang:coactions} {\sc A. Van Daele \&\ Y. Zhang},
   {\em Galois theory for Multiplier Hopf algebras with integrals}\@.
   Algebras and Representation theory, {\bf 2}, 83-106 (1999).

\bibitem{FonsWor:QE2} {\sc A. Van Daele \&\ S.L. Woronowicz},
   {\em Duality for the Quantum $E(2)$ Group}\@.
   Pacific Journal of Math.\ {\bf 173}, No.\ 2, 375-385 (1996).

\bibitem{FonsSabine} {\sc A. Van Daele \&\ S. Van Keer},
   {\em The Yang-Baxter and Pentagon equation}\@.
   Compositio Math.\ {\bf 91}, 201-221 (1994).

\bibitem{VaksKor:QE2} {\sc L.L. Vaksman \&\ L.I.
         Korogodski\u{\i}},
         {\em An algebra of bounded functions on the quantum group of motions
              of the plane, and $q$-analogues of Bessel functions}\@.
         Soviet Math. Dokl. {\bf 39}, 173-177 (1989).

\bibitem{wolfram} {\sc S. Wolfram},
   {\em Mathematica, a system for doing mathematics by computer}\@.
   Addison-Wesley (1993).

\bibitem{Wor:matrix} {\sc S.L. Woronowicz},
   {\em Compact Matrix Pseudo Groups}\@.
   Comm.\ Math.\ Phys.\ {\bf 111}, 613-665 (1987).

\bibitem{Wor:QE2} {\sc S.L. Woronowicz},
   {\em Quantum $E(2)$ group and its Pontryagin dual}\@.
   Lett.\ in Math.\ Phys.\ {\bf 23}, 251-263 (1991).

\bibitem{Wor:Affiliated} {\sc S.L. Woronowicz},
   {\em Unbounded elements affiliated with \Cstar-algebras and non-compact quantum groups}\@.
   Comm.\ Math.\ Phys.\ {\bf 136}, 399-432 (1991).

\bibitem{Wor:operatoreq} {\sc S.L. Woronowicz},
   {\em  Operator equalities related to the quantum $E(2)$ group}\@.
         Commun. Math. Phys. {\bf 144}, 417-428 (1992).
\end{thebibliography}
